Reanalysis Step 2: Multiple Imputation

### 2025-08-30 reanalysis-2-multiple_imputation.qmd
attempt 2l.pan

# Temporal VA variables
custom_methods["baseline_VA_logMAR"] <- "pmm"  # Impute if missing
custom_methods["intermediate_VA_logMAR"] <- "pmm"  # IMPUTE intermediate values
custom_methods["outcome_VA_logMAR"] <- "pmm"  # Impute 2-year outcomes
custom_methods["cohort_id"] <- ""  # Never impute - data management indicator only

@@

# Don't use IDs as predictors AND don't impute them
pred_matrix[, "e_mrn_deidentified"] <- 0
pred_matrix["e_mrn_deidentified", ] <- 0
pred_matrix[, "row_id"] <- 0
pred_matrix["row_id", ] <- 0

>>>>

# Temporal VA variables - use 2l.pan for clustered imputation
custom_methods["baseline_VA_logMAR"] <- "2l.pan"  # Clustered imputation
custom_methods["intermediate_VA_logMAR"] <- "2l.pan"  # Clustered imputation
custom_methods["outcome_VA_logMAR"] <- "2l.pan"  # Clustered imputation
custom_methods["cohort_id"] <- ""  # Never impute - data management indicator only

@@

# Don't use IDs as predictors AND don't impute them
# EXCEPT: e_mrn_deidentified is set to -2 as cluster indicator for 2l methods
pred_matrix[, "e_mrn_deidentified"] <- -2  # Cluster indicator for 2l.pan
pred_matrix["e_mrn_deidentified", ] <- 0  # Don't predict e_mrn itself
pred_matrix[, "row_id"] <- 0
pred_matrix["row_id", ] <- 0
